Goes Here

### 2012-07-31 paper.tex
add figures

\usepackage{caption}
\usepackage{subcaption}

\title{Goes Here}

@@

 \teaser{
   \begin{subfigure}[b]{0.3\textwidth}
	\centering
%    	\includegraphics[width=\textwidth]{a}
      	\caption{}
        \label{teaser:original}
        \end{subfigure}
        ~ 
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
%    	\includegraphics[width=\textwidth]{a}
                \caption{}
                \label{teaser:ours}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
%    	\includegraphics[width=\textwidth]{a}
                \caption{}
                \label{teaser:makerbot}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
%    	\includegraphics[width=\textwidth]{a}
                \caption{}
                \label{teaser:objet}
        \end{subfigure}
        \caption{A textured mesh printed with different types of 3D printers.
        	(a)original model.(b)printed with our printer.(c)makerbot.
        	(d)objet}\label{teaser}
 }

@@

\section{Optimization}

@@

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
 %	\includegraphics[width=\textwidth]{Spec2FabData.png}
   	\caption{}
    \label{fig:ssOrigin}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
%  	\includegraphics[width=\textwidth]{a}
    \caption{b}
    \label{fig:ssPrint}
\end{subfigure}
\caption{Subsurface Scattering. (a)Original object. (b)Printed model.}
\label{fig:SS}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
% 	\includegraphics[width=\textwidth]{a}
   	\caption{}
    \label{fig:deformPhoto}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
%  	\includegraphics[width=\textwidth]{a}
    \caption{}
    \label{fig:deformPrint}
\end{subfigure}
\caption{Matching deformation. (a)photo of a slab being pushed. (b)Printed model being pushed.}
\label{fig:deform}
\end{figure}

@@

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
% 	\includegraphics[width=\textwidth]{a}
   	\caption{}
    \label{fig:ssErr}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
%  	\includegraphics[width=\textwidth]{a}
    \caption{}
    \label{fig:deformErr}
\end{subfigure}
\caption{Error plots for 
optimizing subsurface-scattering and deformation properties 
iteratively. (a)Subsurface scattering errors. (b)Deformation errors.}
\label{fig:err}
\end{figure}

@@

\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height. Loaded dice.

>>>>

\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\title{Goes Here}

@@

 \teaser{
   \begin{subfigure}[b]{0.3\textwidth}
	\centering
    	\includegraphics[width=0.6\textwidth]{figure/bunny_orig.png}
      	\caption{}
        \label{teaser:original}
        \end{subfigure}
        ~ 
        \begin{subfigure}[b]{0.18\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print1.jpg}
                \caption{}
                \label{teaser:ours}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print2.jpg}
                \caption{}
                \label{teaser:makerbot}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.18\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/bunny_print3.jpg}
                \caption{}
                \label{teaser:objet}
        \end{subfigure}
        \caption{A textured mesh printed with different types of 3D printers.
        	(a)original model.(b)printed with our printer.(c)makerbot.
        	(d)objet}\label{teaser}
 }

@@

\subsection{Optimization}

@@

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
A figure showing a material with a particular
look and deformation properties is shown in Figure~\ref{fig:deform}

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
 	\includegraphics[width=\textwidth]{figure/slab_origin.png}
   	\caption{}
    \label{fig:deformPhoto}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
  	\includegraphics[width=\textwidth]{figure/slab_deform.png}
    \caption{}
    \label{fig:deformPrint}
\end{subfigure}
\caption{Simutaneously matching appearance and deformation. 
(a)Original slab of a particular looking. (b)printed slab 
with the same looking and desired deformation.}
\label{fig:deform}
\end{figure}

@@

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
 	\includegraphics[width=\textwidth]{figure/error.pdf}
   	\caption{}
    \label{fig:ssErr}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
  	\includegraphics[width=\textwidth]{figure/error.pdf}
    \caption{}
    \label{fig:deformErr}
\end{subfigure}
\caption{Error plots for 
optimizing subsurface-scattering and deformation properties 
iteratively. (a)Subsurface scattering errors. (b)Deformation errors.}
\label{fig:err}
\end{figure}

@@

We expand gamut of printable colors by stacking translucent materials. We then applied
dithering with our expanded colors.
\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height.

A plot of bounce height after each iteration.

Loaded dice. It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.

\begin{table}
\centering
  \begin{tabular}{ |c| p{0.7in} | p{0.7in} | }
  \hline
  face & simulated probability & measured probability\\
  \hline
  1 & 0.5 & 0.5\\
  \hline
  2 & 0.1 & 0.1\\
  \hline
  3 & 0.1 & 0.1\\
  \hline
  4 & 0.1 & 0.1\\
  \hline
  5 & 0.1 & 0.1\\
  \hline
  6 & 0.1 & 0.1\\

  \hline
  \end{tabular}
  \caption{Simulated and measured dice probability}
  \label{tab:dice}
\end{table}

A plot of simulated probability of landing on "1" after each iteration.
